A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Fixes and comment in Methods

\author{Mathieu Dugr\'e, Val\'erie Hayot-Sasson, Tristan Glatard\\
Department of Computer Science and Software Engineering\\
Concordia University, Montr\'eal, Qu\'ebec, Canada 
\vspace*{0.8cm}
}

@@

In the past few years, neuroimaging has entered the Big Data era due to the
joint increase in image resolution, data sharing, and study sizes. However,
no particular Big Data framework has emerged in this field, and several
alternatives remain available. We compare two popular Big Data frameworks
with Python APIs, Apache Spark and Dask, for their runtime performance in
processing neuroimaging pipelines. Our evaluation uses two synthetic
pipelines processing the 76~GB Big Brain image, and a real pipeline
processing anatomical data from more than 1,000 subjects. We benchmark these pipelines using
 various combinations of task durations, data sizes, and numbers of workers,
deployed on a 64-node compute cluster in Compute Canada's Arbutus
cloud. We evaluate PySpark's RDD API against Dask's Bag, Delayed and Futures.
Results show that despite slight differences between Spark and Dask, both
frameworks perform comparably. However, Dask pipelines risk being limited
by Python's GIL depending on task type and cluster configuration. In all
cases, the major limiting factor was data transfer. While either framework
is suitable for neuroimaging pipelines, more effort needs to be placed in
reducing data transfer time.
\end{abstract}

@@

As data transfers in Big Data workflows are an important source of performance
bottlenecks, Spark incorporates the concepts of data locality and in-memory 
computing. Data locality, introduced by MapReduce~\cite{dean2008mapreduce},
schedules
tasks as close as possible to where the data is storage. In-memory computing
ensures data is maintained in memory whenever possible, as writing large 
amounts data to slower storage devices may be costly. To reduce any unnecessary
communication and computation, Spark also included lazy evaluation, which
builds the entire task graph prior to execution to determine what needs to be
computed.

% Didn't mention Kubernetes as it's still experimental
Spark is compatible with three different schedulers: Spark
standalone, YARN and Mesos.
The Spark standalone scheduler is a simple default scheduler built into Spark.
In contrast, the YARN scheduler is primarily designed to schedule Hadoop-based 
workflows, whereas Mesos can be used to schedule
a variety of different workflows. As scientific researchers would likely be
executing their workflows in HPC environments with neither YARN or Mesos
installed, we limit our focus to Spark's Standalone scheduler.

The Spark Standalone scheduler is composed of three main processes: the
\emph{master}, the \emph{workers} (\emph{slaves}, in Spark) and the
\emph{driver}. The \emph{master} coordinates resources provisioned by
\emph{worker} processes on the cluster. The application is submitted to the
\emph{driver} that in turn requests workers to the master and dispatches tasks
to them. A job is divided into stages to be executed in a different process onto
the workers. Each stage's operation is represented as a high-level task in the
computation graph. The Spark standalone scheduler uses a FIFO 
(First-In-First-Out) job scheduling policy. The Spark standalone scheduler has
two execution modes: client mode, where the driver runs in a dedicated process
outside of the Spark cluster, and cluster mode, where the driver runs within
a worker process. Our experiments use client mode as cluster mode is not
available in PySpark.

@@

\subsubsection{Dask} Dask is a Python-based Big Data engine that is becoming
increasingly popular in the scientific Python ecosystem. Like Spark, Dask avoids data transfers and needless computation and communication through
in-memory computing, data locality, lazy evaluation. Dask worklflows can 
further reduce data transfer costs by leveraging multithreading whenever 
communication is not bounded by Python's GIL. Dask relies on data 
lineage to achieve fault tolerance, however, unlike Spark, does not require
operations to be coarse grained. Furthermore, Dask is lightweight and modular,
allowing users to only install the components they require.

Dask has five main data structure APIs:
Array, Bag, DataFrame, Delayed, and Futures. A Dask
\href{https://docs.dask.org/en/latest/array.html}{Array} is used for the
processing of large arrays. It provides a distributed clone of the popular NumPy
library. Similar to Spark's RDD, a Dask
\href{https://docs.dask.org/en/latest/bag.html}{Bag} is a parallel
collection of Python objects. It offers a programming abstraction similar to the
\href{https://toolz.readthedocs.io/en/latest/}{PyToolz library}. A
\href{https://docs.dask.org/en/latest/dataframe.html}{Dataframe} is a parallel
composition of
\href{http://pandas.pydata.org/pandas-docs/stable/reference/api/pandas.DataFrame.html}{Pandas Dataframes} used to process a large amount of tabular data.
\href{https://docs.dask.org/en/latest/delayed.html}{Delayed} supports
arbitrary tasks
that do not fit in the Array, DataFrame or Bag APIs. Finally,
\href{https://docs.dask.org/en/latest/futures.html}{Futures} are similar to
Delayed in that they support arbitrary tasks, but they operate in real-time
rather than lazily. With the exception of Dask Bag, all APIs, by default, use
the local multithreaded scheduler. Dask Bag, instead, relies on the local
multiprocessing scheduler.  All Dask data structure APIs, with the exception of
Dask Array and Dask DataFrame, were used in our experiments.

The Dask graph is the internal representation of Dask application to be
executed  by the scheduler. API Operations generate multiple small tasks in
the computation graph allowing an easier representation of complex
algorithms.

@@

 We used Compute Canada's
 \href{https://docs.computecanada.ca/wiki/Cloud\_resources}{Arbutus Cloud} operated by
 the \href{https://www.westgrid.ca}{WestGrid} regional organization at the University
 of Victoria, running OpenStack Queens release. We used c8-30gb-186 cloud
 instances with 8 VCPUs, an Intel Xeon Gold 6130 processor, \SI{30}{\giga\byte} of
 RAM at \SI{2666}{\mega\hertz}, \SI{20}{\giga\byte} of mounted storage, and a base
 image running CentOS 7.5.1804 with Linux kernel version
 3.10.0\-862.11.6.el7.x86\_64. Instances are connected by a
 \SI{10}{\giga\bit/\second} Ethernet network.

@@

 One cloud instance did not host any worker and had a \SI{2}{\tera\byte} disk volume
 shared with the other instances using the Network File System (NFS) v4.
 This instance was also used for the Spark driver and master, for the
 Dask scheduler, and for job monitoring with the Spark and Dask user
 interfaces. For both Spark and Dask, spilled data is evicted to the NFS.

@@

We used BigBrain~\cite{Amunts:13}, a three-dimensional image of a human
brain with voxel intensities ranging from 0 to 65,535. The original data is
stored in 125 blocks in the MINC~\cite{minc} HDF5-based format, available
at \url{ftp://bigbrain.loris.ca/BigBrainRelease.2015/3D\_Blocks/40um} at a
resolution of \SI{40}{\micro\metre}. We converted the blocks into the
\href{https://nifti.nimh.nih.gov/nifti-1}{NifTI} format, a popular format
in neuroimaging. We left the NifTI blocks uncompressed, resulting in 
a total data size of \SI{81}{\giga\byte}. 
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of 
\SI{2.7}{\giga\byte}, \SI{0.648}{\giga\byte}, and
\SI{0.108}{\giga\byte}, using the sam~\cite{sam} library.

We also used the dataset provided by the Consortium for Reliability and
Reproducibility (\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR}) as
available on \href{http://datasets.datalad.org/?dir=/corr/RawDataBIDS}{DataLad}. The
entire dataset is \SI{408.4}{\giga\byte}, containing anatomical, diffusion and
functional images of 1,397 subjects acquired in 29 sites. We used all 3491 anatomical
images, representing \SI{39}{\giga\byte} overall (\SI{11.17}{\mega\byte} per image on
average).

@@

\begin{algorithm}[!b]
    \caption{Incrementation (adapted from~\cite{hayot2019performance})}\label{alg:incrementation}
    \begin{algorithmic}
    \Require{\(x\), a sleep delay in float}
    \Require{\(file\), a file containing a block}
    \Require{\(fs\), NFS to write image to.}
    \State{Read \(block\) from \(file\)}
    \ForEach{\(i \in iterations\)}
        \ForEach{\(block \in image\)}
            \State{\(block\gets block+1\)}
            \State{Sleep \(x\)}
        \EndFor
    \EndFor
    \State{Write \(block\) to \(fs\)}
\end{algorithmic}
\end{algorithm}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2cm, height=\columnwidth,
    angle=-90]{images/incrementation-task-graph.png}
    \caption{Task graph for Incrementation with 5 iterations and 3 BigBrain blocks.
    Circles represent the incrementation and sleep function while rectangles
    represent stages of the blocks.}\label{fig:tg-inc}
\end{figure}

@@

 Our second application calculates the histogram of the BigBrain image (see
 Algorithm~\ref{alg:histogram}). It reads the image blocks from the shared file
 system, calculates intensity frequencies, aggregates the frequencies across the
 blocks, and finally writes the resulting histogram to the shared file system as a
 single \SI{766}{\kilo\byte} file. It follows the map-reduce
 paradigm, in which the final result is obtained from all the input blocks (see
 Fig.~\ref{fig:tg-histo}). This application requires data shuffling, incurring 
 additional performance costs compared to Algorithm~\ref{alg:incrementation}.
 The total amount of shuffled data is, however, limited to
 \SI{2.62}{\mega\byte} per blocks as it only consists of image histograms.
Two implementation are studied: pure Python and NumPy.

\begin{algorithm}[!t]
    \caption{Histogram}\label{alg:histogram}
    \begin{algorithmic}
    \Require{\(files\), files containing BigBrain}
    \Require{\(fs\), NFS to save image to.}
    \ForEach{\(file \in files\)}
        \State{Read \(block\) from \(file\)}
        \State{{Calculate \(frequency\) of \(blocks\)}}
    \EndFor

    \State{\(histogram\gets\)Aggregate \(frequency\) of each \(file\)}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2cm, height=\columnwidth,
    angle=-90]{images/histogram-task-graph.png}
    \caption{Task graph for Histogram with 3 BigBrain blocks. Circles represent the
    functions while rectangles represent stages of the blocks.
    }\label{fig:tg-histo}
\end{figure}

@@

For this experiment, we used the
\href{https://github.com/BIDS-Apps/example}{BIDS app example} map-reduce style 
application. The map phase, also called participant analysis, extracts the brain
tissues of a subject's 3D MRI using the FMRIB Software Library
(\href{https://fsl.fmrib.ox.ac.uk/fsl/fslwiki}{FSL}), and writes the resulting
image (\SI{2.47}{\mega\byte} on average) to the NFS. The reduce phase, or group
analysis, computes the volume of each brain and returns the average
volume, shuffling a total of \SI{8.6}{\giga\byte} image data.

While Incrementation and Histogram were implemented directly in Python, the 
BIDS App example requires an external library and is distributed as a Docker container image
(bids/base\_fsl on DockerHub). We converted the Docker image to a Singularity image,
given its popularity for HPC and reproducibility, using
\href{https://hub.docker.com/r/singularityware/docker2singularity/tags/}{docker2singularity}.
The image was preloaded on the NFS and singularity version 3.2.1\-1.el7 was installed
on all instances. Due to a bug in the conversion from Docker to Singularity, we had to
export the path for FSL.

@@

The four parameters were varied in our experiments, as shown in
Table~\ref{tab:param}. We varied (1) the number of workers to assess the
scalability of the engines, (2) the number of BigBrain blocks in
Incrementation and Histogram to measure the effect of different IO patterns
and parallelization degrees, and (3) the number of iterations and sleep
delay in Incrementation to evaluate the effect of job length and number of
tasks.
It should be noted that increasing the number of blocks or iterations also
increases the total compute time of the application for a given sleep
delay. To avoid any potential external bias such as background load on the
network, we ran the experiments in a randomized order and cleared the page
cache of each worker before each execution.

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead across all application
tasks. 
The overhead calculation for each CPU is the end time of its last processed task
minus the start time of the application. The summation of those results is the
total overhead.

@@

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan of the Incrementation application
for different numbers of workers and engines. The bars show the average
makespan over 3 repetitions while the error bars are the standard deviation. Overall,
there is no substantial makespan difference between the engines. Dask seems to have a
slight advantage over Spark, \SI{83.61}{\second} on average,
with Delayed and Futures being slightly better than Bag.

>>>>

\author{Mathieu Dugr\'e, Val\'erie Hayot-Sasson, Tristan Glatard\\
Department of Computer Science and Software Engineering\\
Concordia University, Montr\'eal, Qu\'ebec, Canada 
\vspace*{0.8cm} % to avoid weird spacing of 1st page by Latex.
}

@@

In the past few years, neuroimaging has entered the Big Data era due to the
joint increase in image resolution, data sharing, and study sizes. However,
no particular Big Data framework has emerged in this field, and several
alternatives remain available. We compare two popular Big Data frameworks
with Python APIs, Apache Spark and Dask, for their runtime performance in
processing neuroimaging pipelines. Our evaluation uses two synthetic
pipelines processing the 81~GB Big Brain image, and a real pipeline
processing anatomical data from more than 1,000 subjects. We benchmark these pipelines using
 various combinations of task durations, data sizes, and numbers of workers,
deployed on a 64-node compute cluster in Compute Canada's Arbutus
cloud. We evaluate PySpark's RDD API against Dask's Bag, Delayed and Futures.
Results show that despite slight differences between Spark and Dask, both
frameworks perform comparably. However, Dask pipelines risk being limited
by Python's GIL depending on task type and cluster configuration. In all
cases, the major limiting factor was data transfer. While either framework
is suitable for neuroimaging pipelines, more effort needs to be placed in
reducing data transfer time.
\end{abstract}

@@

As data transfers in Big Data workflows are an important source of performance
bottlenecks, Spark incorporates the concepts of data locality and in-memory 
computing. Data locality, popularized by MapReduce~\cite{dean2008mapreduce},
schedules
tasks as close as possible to where the data is stored. In-memory computing
ensures data is maintained in memory whenever possible, as writing large 
amounts data to slower storage devices may be costly. To reduce any unnecessary
communication and computation, Spark also included lazy evaluation, which
builds the entire task graph prior to execution to determine what needs to be
computed.

% Didn't mention Kubernetes as it's still experimental
Spark is compatible with three different schedulers: Spark
standalone, YARN and Mesos.
The Spark standalone scheduler is a simple default scheduler built into Spark.
In contrast, the YARN scheduler is primarily designed to schedule Hadoop-based 
workflows, whereas Mesos can be used to schedule
a variety of different workflows. As researchers would likely be
executing their workflows in HPC environments with neither YARN or Mesos
installed, we limit our focus to Spark's Standalone scheduler.

The Spark Standalone scheduler is composed of three main processes: the
\emph{master}, the \emph{workers} (\emph{slaves}, in Spark) and the
\emph{driver}. The \emph{master} coordinates resources provisioned by
\emph{worker} processes on the cluster. The application is submitted to the
\emph{driver} that in turn requests workers to the master and dispatches tasks
to them. A job is divided into stages to be executed in a different process onto
the workers. Each stage's operation is represented as a high-level task in the
computation graph. The Spark standalone scheduler uses a FIFO 
(First-In-First-Out) job scheduling policy, and it has
two execution modes: client mode, where the driver runs in a dedicated process
outside of the Spark cluster, and cluster mode, where the driver runs within
a worker process. Our experiments use client mode as cluster mode is not
available in PySpark.

@@

\subsubsection{Dask} Dask is a Python-based Big Data engine that is becoming
increasingly popular in the scientific Python ecosystem. Like Spark, Dask avoids data transfers and needless computation and communication through
in-memory computing, data locality, and lazy evaluation. Dask worklflows can 
further reduce data transfer costs by leveraging multithreading whenever 
communication is not bounded by Python's GIL. Dask relies on data 
lineage to achieve fault tolerance, however, unlike Spark, does not require
operations to be coarse grained. Furthermore, Dask is lightweight and modular,
allowing users to only install the components they require.

Dask has five main data structures:
\href{https://docs.dask.org/en/latest/array.html}{Array}, \href{https://docs.dask.org/en/latest/bag.html}{Bag},
\href{https://docs.dask.org/en/latest/dataframe.html}{DataFrame},
 \href{https://docs.dask.org/en/latest/delayed.html}{Delayed}, 
 and \href{https://docs.dask.org/en/latest/futures.html}{Futures}. A Dask
Array is used for the
processing of large arrays. It provides a distributed clone of the popular NumPy
library. Similar to Spark's RDD, a Dask
Bag is a parallel
collection of Python objects. It offers a programming abstraction similar to the
\href{https://toolz.readthedocs.io/en/latest/}{PyToolz library}. A Dask
Dataframe is a parallel
composition of
\href{http://pandas.pydata.org/pandas-docs/stable/reference/api/pandas.DataFrame.html}{Pandas Dataframes},
 used to process a large amount of tabular data.
Dask Delayed supports
arbitrary tasks
that do not fit in the Array, DataFrame or Bag APIs. Finally,
Dask Futures are similar to
Delayed in that they support arbitrary tasks, but they operate in real-time
rather than lazily. With the exception of Dask Bag, all APIs, by default, use
the local multithreaded scheduler. Dask Bag, instead, relies on the local
multiprocessing scheduler.  All Dask data structures, with the exception of
Dask Array and Dask DataFrame, were used in our experiments.

The Dask graph is the internal representation of a Dask application to be
executed  by the scheduler. API operations generate multiple small tasks in
the computation graph, allowing an easier representation of complex
algorithms.

@@

 We used Compute Canada's
 \href{https://docs.computecanada.ca/wiki/Cloud\_resources}{Arbutus Cloud} operated by
 the \href{https://www.westgrid.ca}{WestGrid} regional organization at the University
 of Victoria, running OpenStack Queens release. We used c8-30gb-186 cloud
 instances with 8 VCPUs, an Intel Xeon Gold 6130 processor, \SI{30}{\giga\byte} of
 RAM at \SI{2666}{\mega\hertz}, \SI{20}{\giga\byte} of mounted storage, and a base
 image running CentOS 7.5.1804 with Linux kernel version
 3.10.0\-862.11.6.el7.x86\_64. Instances were connected by a
 \SI{10}{\giga\bit/\second} Ethernet network.

@@

 One cloud instance did not host any worker and had a \SI{2}{\tera\byte} disk volume
 shared with the other instances using the Network File System (NFS) v4.
 This instance was also used for the Spark driver and master, for the
 Dask scheduler, and for job monitoring with the Spark and Dask user
 interfaces. For both Spark and Dask, spilled data was evicted to the NFS.

@@

We used BigBrain~\cite{Amunts:13}, a three-dimensional image of a human
brain with voxel intensities ranging from 0 to 65,535. The original data is
stored in 125 blocks in the MINC~\cite{minc} HDF5-based format, available
at \url{ftp://bigbrain.loris.ca/BigBrainRelease.2015/3D\_Blocks/40um} at a
resolution of \SI{40}{\micro\metre}. We converted the blocks into the
\href{https://nifti.nimh.nih.gov/nifti-1}{NifTI} format, a popular format
in neuroimaging. We left the NifTI blocks uncompressed, resulting in 
a total data size of \SI{81}{\giga\byte}. 
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of 
\SI{2.7}{\giga\byte}, \SI{0.648}{\giga\byte}, and
\SI{0.108}{\giga\byte}, using the \href{https://github.com/big-data-lab-team/sam}{sam} library.

We also used the dataset provided by the Consortium for Reliability and
Reproducibility (\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR}~\cite{zuo2014open}) as
available on \href{http://datasets.datalad.org/?dir=/corr/RawDataBIDS}{DataLad}. The
entire dataset is \SI{408.4}{\giga\byte}, containing anatomical, diffusion and
functional images of 1,397 subjects acquired in 29 sites. We used all 3,491 anatomical
images, representing \SI{39}{\giga\byte} overall (\SI{11.17}{\mega\byte} per image on
average).

@@

\begin{algorithm}[!b]
    \caption{Incrementation (adapted from~\cite{hayot2019performance})}\label{alg:incrementation}
    \begin{algorithmic}
    \Require{\(x\), a sleep delay in float}
    \Require{\(file\), a file containing a BigBrain block}
    \Require{\(fs\), NFS mount to write image to}
    \State{Read \(block\) from \(file\)}
    \ForEach{\(i \in iterations\)}
        \ForEach{\(block \in image\)}
            \State{\(block\gets block+1\)}
            \State{Sleep \(x\)}
        \EndFor
    \EndFor
    \State{Write \(block\) to \(fs\)}
\end{algorithmic}
\end{algorithm}

\begin{figure}[!b]
    \centering
    \includegraphics[height=\columnwidth,
    angle=-90]{images/incrementation-task-graph.png}
    \caption{Task graph for Incrementation with 5 iterations and 3 BigBrain blocks.
    Circles represent the incrementation and sleep function while rectangles
    represent data elements.}\label{fig:tg-inc}
\end{figure}

@@

 Our second application calculates the histogram of the BigBrain image (see
 Algorithm~\ref{alg:histogram}). It reads the image blocks from the shared
 file system, calculates intensity frequencies, aggregates the frequencies
 across the blocks, and finally writes the resulting histogram to the
 shared file system as a single \SI{766}{\kilo\byte} file. It follows the
 map-reduce paradigm, in which the final result is obtained from all the
 input blocks (see Fig.~\ref{fig:tg-histo}). This application requires data
 shuffling, incurring additional performance costs compared to
 Algorithm~\ref{alg:incrementation}. The total amount of shuffled data is,
 however, limited to \SI{2.62}{\mega\byte} per blocks as it only consists
 of image histograms. Two implementation are studied: a pure Python one,
 where frequencies are computed through Python dictionary manipulations, and one based
 on the \href{https://github.com/numpy}{NumPy} library, that implements array computations in C.

\begin{algorithm}[!t]
    \caption{Histogram}\label{alg:histogram}
    \begin{algorithmic}
    \Require{\(files\), files containing BigBrain blocks}
    \Require{\(fs\), NFS mount to save image to}
    \ForEach{\(file \in files\)}
        \State{Read \(block\) from \(file\)}
        \State{{Calculate \(frequencies\) in \(block\)}}
    \EndFor

    \State{\(histogram\gets\)Aggregate \(frequencies\) of each \(file\)}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[height=\columnwidth,
    angle=-90]{images/histogram-task-graph.png}
    \caption{Task graph for Histogram with 3 BigBrain blocks. Circles represent the
    functions while rectangles represent data elements.
    }\label{fig:tg-histo}
\end{figure}

@@

We used the
\href{https://github.com/BIDS-Apps/example}{BIDS app example} map-reduce style 
application. The map phase, also called participant analysis, extracts the brain
tissues of a subject's 3D MRI from the CoRR dataset using the FMRIB Software Library
(\href{https://fsl.fmrib.ox.ac.uk/fsl/fslwiki}{FSL}), and writes the resulting
image (\SI{2.47}{\mega\byte} on average) to the NFS. The reduce phase, or group
analysis, computes the volume of each brain and returns the average
volume, shuffling a total of \SI{8.6}{\giga\byte} image data.

While Incrementation and Histogram were implemented directly in Python, the 
BIDS App example requires an external set of command-line tools distributed as a Docker container image
(bids/base\_fsl on DockerHub). We converted the Docker image to a Singularity image for use in 
an HPC environment, using
\href{https://hub.docker.com/r/singularityware/docker2singularity/tags/}{docker2singularity}.
The image was preloaded on the NFS and Singularity version 3.2.1\-1.el7 was installed
on all instances.

@@

Four parameters were varied in our experiments, as shown in
Table~\ref{tab:param}. We varied (1) the number of workers, to assess the
scalability of the engines, (2) the number of BigBrain blocks in
Incrementation and Histogram, to measure the effect of different I/O patterns
and parallelization degrees, and (3) the number of iterations and sleep
delay in Incrementation, to evaluate the effect of job length and number of
tasks.
It should be noted that increasing the number of blocks or iterations also
increases the total compute time of the application for a given sleep
delay. To avoid any potential external bias such as background load on the
network, we ran the experiments in a randomized order and cleared the page
cache of each worker before each execution.

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead times across all application
tasks. 
The overhead calculation for each CPU is the end time of its last processed task
minus the start time of the application. The summation of those results is the
total overhead. \TG{This last sentence looks wrong to me.}

@@

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan of the Incrementation application
for different numbers of workers and engines. The bars show the average
makespan over 3 repetitions while the error bars are the standard deviations. Overall,
there is no substantial makespan difference between the engines. Dask seems to have a
slight advantage over Spark, \SI{83.61}{\second} on average,
with Delayed and Futures being slightly better than Bag.
